An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/intro.tex
intro

In order to overcome these obstacles,
researchers have proposed 
statistical analysis and learning-based approaches%
~\cite{wang04automatic, zhang14encore, yuan11context}. 
These efforts build checking policies by learning from a sample 
data set, rather than explicitly specifying entries' types or rules.
In particular, for each entry in a certain configuration file, 
if it deviates from common values used in a large collection
of configuration files (\ie, the data set for training), it is typically
suspected to contain a potential configuration error.
However, because these learning 
efforts {\em either} are limited to simplistic 
configuration errors (\eg, type errors and syntax errors)
{\em or} heavily rely on template-based inference~\cite{zhang14encore}, 
many sophisticated configuration errors, 
which are difficult to template in practice, cannot be detected.
For example, if {\tt extension = mysql.so} appears 
before {\tt extension = recode.so} in a PHP configuration file,  
it would lead to a crash error, since the correct ordering 
should be {\tt extension = recode.so} before 
{\tt extension = mysql.so}~\cite{yin11anempirical};
however, such an error cannot be detected by existing
learning efforts, since it is hard to build a corresponding template ~\cite{xu15systems}.

@@

In order to truly achieve automatic configuration verification,
we argue that we need to leverage a collection of more powerful learning 
algorithms (not necessarily depending on templates) to derive 
a more sophisticated language model (with abundant rules covering
tricky configuration errors), and then check the configuration files
of interest through the learned language model. \jon{Too many parentheses in sentence. Cut down}

>>>>

To overcome these obstacles, researchers have proposed approaches based on
a statistical analysis and learning~\cite{wang04automatic, zhang14encore, yuan11context}
that try to infer the rules and policies how configuration files are constructed.
Rather than explicitly specifying entries' types or rules, these research directions are focused
on learning policies from a sample data set.
The learned rules are usually constructed along the following pattern: for every entry in a configuration file, 
we check if it deviates from a ``typical'' value, \ie a value computed from a large training set consisting of configuration files.
If the entry is significantly different that the typical value, we suspect that it could be a potential configuration error.
The downside of this approach is that these learning efforts are limited to simplistic 
configuration errors, such as type errors and syntax errors, or they 
heavily rely on template-based inference~\cite{zhang14encore}. As we pointed out earlier, since configuration files are not written in a typed language with a fixed syntax,
type errors and syntax errors are relatively rare and easy to detect. However, many sophisticated configuration errors, 
which are difficult to template in practice, cannot be detected this way. As an illustration of such an error consider the ordering errors, which
happen when some entries are inserted in a wrong order. 
For example, if in a PHP configuration file an entry {\tt extension = mysql.so} appears 
before {\tt extension = recode.so},  
it would lead to a crash error, where the Apache server cannot start due to the segmentation fault error. The correct ordering 
should be {\tt extension = recode.so} before 
{\tt extension = mysql.so}~\cite{yin11anempirical}.
These types of errors cannot be detected by existing
learning efforts, since it is hard to build a corresponding template ~\cite{xu15systems}: we would need to capture ordering relations of all the entries. Some of 
them can appear in an arbitrary ordering and the resulting templates would be too large and not efficient for a practical use.

@@

In this paper we present \app, the first automatic verification framework
for general software configurations. \app is based a collection of more powerful learning 
algorithms, that do not necessarily depend on templates. The learning process can be seen as a process of deriving  
a specification of configuration files, from a dataset containing a large sample of configuration files. In order to do that
we utilize a more sophisticated language model. Thus, in the first step \app analyzes the given dataset and generates a 
well-structured and probabilisticly-typed 
intermediate representation.

which aims to truly  achieve automatic configuration verification. we need to leverage a collection of more powerful learning 
algorithms, that do not necessarily depend on templates. In order to do that
there should be a more sophisticated language model, to which we would translate configuration files' entries.
Based on  the learned language model we would develop an abundant set of rules covering 
complex configuration errors. The set of learned rules should be accurate and we should be able to efficiently check 
the configuration files
of interest.
